\documentclass[12pt,letterpaper]{letter}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Chris Cox}
\title{Depth Prelim}
\begin{document}
Dear Committee Members,

Thank you for reviewing this work as the depth component of my preliminary examination. While I am comfortable calling this work my own, the paper was decidedly co-authored by Tim Rogers, whose invaluable guidance and craftsmanship helped to shape my initial efforts into a polished manuscript. In light of this, I would like to briefly discuss Tim and my relative contributions to this document.

Our writing process was iterative, such that nearly every aspect of the paper was drafted by me before Tim provided feedback or contributed revisions. A notable exception is Figure 1 and it's caption, which depict and describe Rogers et al.'s (2004) model of semantic memory, which were both composed by Tim. I reviewed the relevant literature and studied the computational methods necessary to execute these simulations and analyses. The interpretations of my data documented in this work are the result of many discussions between Tim and I, but ultimately the paper consists of my take on these data. Tim advised on the big-picture structure of the paper in the context of our discussions about our data and it's relevance.

The neural network modeling and subsequent analyses were all my own work.  The seed-idea of training neural networks and treating their activation patterns as neural activity sampled from different anatomical regions was Tim's, but the development of the idea into an application was a joint effort and the implementation my own work.

This paper would not exist if not for Tim and his guidance and support. That said, he and I are comfortable saying this paper is a demonstration of my depth of expertise on computational methods that can be used to advance the field's understanding of the neural representation of concepts. 

Sincerely,

Chris Cox
\end{document}